The impacts of park access on health outcomes: A spatial comprehensive approach

### 2019-02-12 manuscript.Rnw
Complete initial draft of paper

@@

%% Front matter =========================
\title{The impacts of park access on health outcomes: a spatial comprehensive approach}

\author{Nico Boyd\affilnum{1}, Gregory S. Macfarlane\affilnum{2}, and Kari Watkins\affilnum{1}}
\runninghead{Boyd, et al.}

\affiliation{\affilnum{1}School of Civil and Environmental Engineering, Georgia Institute of Technology\\
\affilnum{2}Civil and Environmental Engineering Department, Brigham Young University}

@@

In this paper, we present a holistic and flexible measurement for park
accessibility based in random utility theory. This measure can consider the continuous
distance to all parks in the region, weighted by the size of the park and other
amenities. We apply this measurement to study the link between park
accessibility and attractiveness and Census tract-level aggregate physical
activity participation and obesity rates in New York City, controlling for
spatial correlation and dependence. We find a positive relationship where the
least park-accessible tracts have an expected physical activity participation
rate 3.8 percent lower than the most accessible tracts, controlling for
socioeconomic characteristics. We also find that increased physical activity
rates lead to reduced aggregate obesity rates, but that when controlling for
physical activity rates, accessibility to parks does not reduce overall accessibility.
This suggests that to be an effective tool for addressing chronic diseases,
communities must do more than simply provide parks, but also incentivize more
citizens to use them.

@@

\begin{table*}[ht]
  \caption{Commonly cited benefits of parks and greenspaces}
  \label{tab:parkbenefits}
\begin{tabular}{lp{11cm}}
\toprule
Category & Summary of Benefits\\
\midrule
Physical Health & Provide clean drinking water \citep{Benedict2006}\\
 & Promote faster healing in hospitals \citep{Akbari2001}\\
 & Reduce heat-related mortality \citep{Stone2006}\\
 & Reduce incidence of cardiovascular-related mortality \citep{Mitchell2008}\\
 & Improved air quality and related reductions in respiratory-related mortality \citep{Lovasi2008}\\
\midrule
Mental Health & Reduce stress and mental fatigue \citep{Wolch2014}\\
  & Reduce aggression \citep{Kuo2001a}\\
  & Enhance emotional and cognitive development\\
  & Improve behavioral outcomes in youth \\
\midrule
Social Health & Enhanced community aesthetics\\
 & Reduce crime \citep{Kuo2013,Wolfe2012}\\
 & Increase social interaction \citep{Sullivan2004}\\
\midrule
Economic Health & Provide ecosystem services\\
 & Increase residential property values and municipal property tax revenues\\
 & Attract more shoppers and increase economic activity to commercial districts \\
\bottomrule
\end{tabular}
\end{table*}

@@

To evaluate the impacts of parks and greenspaces on health outcomes at a
sub-metropolitan level, one of the fundamental tasks involved is the selection
of a measure of accessibility. In a comprehensive meta-analysis of published
studies that measure active accessibility (accessibility using non-motorized
travel modes including walking and cycling), \citet{Vale2016} identified four
broad categories of studies based on the metric employed:
\begin{description}
  \item[Distance-based]{Account only for the Euclidean distance between origins
  and destinations}
  \item[Infrastructure-based]{Explicitly incorporate
  relevant transportation networks like roads and sidewalks to more accurately
  measure travel time and distance}
  \item[Gravity-based]{Incorporate travel impedance
  measures to model accessibility as a function of a destination’s attractiveness}
  \item[Walk-score]{Similar to Gravity-based, with the impedance measure
  explicitly designed around walking}
\end{description}

Importantly, \citeauthor{Vale2016} acknowledge that there is not yet a
consensus on the most appropriate accessibility metric to use in a given
setting, noting that ''ways to measure active accessibility are as varied as the
number of scholars the measure them.'' For example, infrastructure-based distances
can vary widely depending on which modes of travel infrastructure are considered.
Similarly, gravity-based measures may not always account for surrounding land
uses when considering the attractiveness or impedance of a destination.
In evaluating methodologies of measuring access to urban services, including
parks and greenspaces, \citet{Logan2017} note that existing and commonly used
approaches "often simplify their measure of proximity by using large areal
units and by imposing arbitrary distance thresholds," which often results in
access-poor populations being overlooked.

@@

\subsection{Data}
This study uses data available to the public from a variety of agencies and
data providers.

@@

The primary dataset is a geographic polygons shapefile of Census tracts in
New York City. We appended relevant sociodemographic data for each tract level
from the American Community Survey 2011-2015 5-year estimates. Data on physical
activity participation rate and obesity rates for each tract are available from
the Centers for Disease Control and Prevention’s 500 Cities Project (WE NEED A CITATION).
After removing tracts with missing population information or outlying and unusual
characteristics, we have Sexpr{nrow(tracts)} complete cases. Table
\ref{tab:tractsdata} presents key descriptive statistics for these data.

@@

In a destination choice framework, the tracts represent the "origins" and
"destinations" are parks in New York City.
We retrieved a shapefile of public parks and greenspaces within New York City’s
municipal boundaries and checked it for accuracy and relevance (WE NEED A CITATION).
Upon inspection,
we removed several facilities that do not qualify as publicly accessible green
space, such as Yankee Stadium and its surrounding parking lots. We also removed
parks of less than half an acre in size, as these appear to be predominantly
vacant lots or parking strips rather than legitimate public green space. This
leaves us with \Sexpr{nrow(parks)} parks. It is worth noting that the particular
dataset classifies specific facilities within larger parks as independent
features: baseball fields within Central Park, for example, are themselves
unique greenspace. We elect to retain these independent features as they may
generate additional activity.

@@

We predict the rate of physical activity ($y$) in a census tract as a
function of the tract's sociodemographic characteristics and choice-based
accessibility to parks with the following  specification:
\begin{equation}\label{eq:themodel}
 y_i = f(\vect{x}_i, CS_i, g(W, \vect{y} \vect{X}))
\end{equation}
where $\vect{x}_i$ is a vector of tract-level sociodemographic attributes,
$CS_i$ is a choice-based
accessibility measure for the tract computed from Equation \ref{eq:cs} and
$g(W, \vect{y}, X)$
represents the impact of spatial neighborhood effects on the outcome.

@@

The researcher must assert $W$ {\em a priori}, though there are several
common specifications \citep{Dubin1998}. In this study we specify that tracts
with centroids located within 1.8 miles of each other are considered neighbors,
and the strength of the relationship is the inverse of the distance between
them:
\begin{equation}\label{eq:weightsrule}
W_{ij} = \begin{cases}
  {\frac{1/d_{ij}} {\sum_{k=1}^n( 1/d_{ik})}} & \text{for $d_{ij} \leq 1.8$ miles}\\
  0  & \text{for $d_{ij} > 1.8$ miles}
  \end{cases}
\end{equation}

<<weights, warning = FALSE>>=
pop_weighted_centroids <- read_csv("data/CenPop2010_Mean_TR36.csv") %>%
  mutate(geoid = str_c(STATEFP, COUNTYFP, TRACTCE))
pop_weighted_centroids <- left_join(tracts@data, pop_weighted_centroids, by = "geoid") %>%
  dplyr::select(geoid, LONGITUDE, LATITUDE) %>%
  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
  st_transform(2263)

tracts.dnn <- dnearneigh(gCentroid(as(pop_weighted_centroids, "Spatial"), byid = TRUE),
                         0, 1.8 * 5280)
dists <- nbdists(tracts.dnn, gCentroid(tracts, byid = TRUE))
dists.inv <- lapply(dists, function(x) 1 / x)
W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv,
              zero.policy = TRUE, style = "W")
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
@

@@

Extant destination choice models used in practice typically use travel time in
minutes as a travel impedance term, and employment by sector as a size term or
attraction component. Typically such models handle recreational trips together with
other non-work and non-school trips, and we therefore can find no previously
estimated coefficients using size terms relevant to park acreage or amenities.
Given this gap in the literature, we instead assert values for $\beta$ to generate
the choice-based accessibility statistic used in this study.

@@

We initially estimated potential values of the $\beta$ coefficients by
applying a limited-memory, box-constrained optimization algorithm maximizing the
SDM model log-likehood \cite. The constraint required that the coefficient on
size be positive and that on distance negative; all else equal, we assert people
will prefer to use larger parks and parks that are nearer to their residence. This
resulted in $\beta_d = -1.98$  and $\beta_s = 0.000$. Though the "most likely"
parameter value, in this case it was unsatisfactory for two reasons: first,
our prior assertion that park size is a valuable attribute of a park, and second
the observation that in this specification tracts bordering on the corners of
Central Park were measured with poor overall accessibility. we subsequently adjusted the $\beta_s$ value
so that the

to a value of $1.00$

@@

@@

@@

The other two models presented in Table \ref{tab:pa_models} include
the log-sum accessibility statistic described in Section
\ref{subsec:accessibility}  added as a predictor. In both income specifications,
the

base model as
well as models including logsum-based accessibility with and without Twitter
activity. A few initial observations can be made from this table. First, adding
the logsum measurement significantly improves the overall model fit, using a
likelihood ratio test on the model log-likelihood statistics. Second, the
coefficient estimates on the controlling variables remain virtually unchanged
from the base model.

@@

\begin{table*}
  \caption{SEM Coefficients Predicting Physical Activity Rates}
  \label{tab:pa_models}
<<pamodelchart, results="asis">>=
termnames <- c("(Intercept)", "log(density)" ,
               "Full-time workers", "College-educated",  "Single Adults",
               "Share of children (0-17)", "Share of young adults (18-29)",
               "Share of seniors (65+)", "Black population share",
               "Asian population share",
               "Hispanic population share", "Other Minorities",
               "Share high income", "Share low income",
               "$\\lambda$", "$\\log($Income$)$",
               "Access logsum")
texreg(pa_models, digits = 4, table = FALSE, single.row = TRUE,
       booktabs = TRUE, use.packages = FALSE,
       custom.coef.names = termnames)
@
\end{table*}

<<obesity_models>>=
obesity_models <- lapply(pa_models, function(model){
  update(update(model, obesity ~ . ))
})

@@

<<screen_obese_models, eval = FALSE>>=
screenreg(obesity_models, digits = 4, table = FALSE,
          stars = c(0.001, 0.01, 0.05, 0.1) )
@
We now consider the impacts of a model where the dependent variable is
the {\em obesity} rate, and physical activity becomes an independent covariate
alongside the controlling variables and the accessibility logsum variable.

\begin{table*}
  \caption{SEM Coefficients Predicting Obesity Rates}
  \label{tab:obese_models}
<<obesemodelchart, results="asis">>=
termnames <- c("(Intercept)", "log(density)" ,
               "Full-time workers", "College-educated",  "Single Adults",
               "Share of children (0-17)", "Share of young adults (18-29)",
               "Share of seniors (65+)", "Black population share",
               "Asian population share",
               "Hispanic population share", "Other Minorities",
               "Share high income", "Share low income",
               "$\\lambda$", "$\\log($Income$)$",
               "Access logsum")
texreg(obesity_models, digits = 4, table = FALSE, single.row = TRUE,
       booktabs = TRUE, use.packages = FALSE,
       custom.coef.names = termnames)
@
\end{table*}

\section{Discussion}

We readily acknowledge limitations in this study. To begin, it would be beneficial
to have estimated the logsum coefficients from a high-quality survey rather than
asserting them to match {\em a priori expectations of}

>>>>

\usepackage{url}

@@

%% Front matter =========================
\title{The impacts of park access on health outcomes: A spatial comprehensive approach}

\author{Nico Boyd\affilnum{1}, Gregory S. Macfarlane\affilnum{2}, Kari Watkins\affilnum{1}, 
and Professor WhogaveTweets\affilnum{3}}
\runninghead{Boyd, et al.}

\affiliation{\affilnum{1}School of Civil and Environmental Engineering, Georgia Institute of Technology\\
\affilnum{2}Civil and Environmental Engineering Department, Brigham Young University\\
\affilnum{3}Somewhere at Georgia Tech}

@@

In this paper, we present a holistic and flexible measurement for park
accessibility based in random utility choice theory. This measure can consider 
the continuous
distance to all parks in the region, weighted by the size of the park and other
amenities. We apply this measurement to study the link between park
accessibility and attractiveness and Census tract-level aggregate physical
activity participation and obesity rates in New York City, controlling for
spatial correlation and tract-level socioeconomic characteristics. 
We find a positive relationship where the
least park-accessible tracts have an expected physical activity participation
rate XX percent lower than the most accessible tracts, though this result is 
only suggestive of correlation from a statistical perspective.
However, we also find a strong and significant negative correlation between 
increased park accessibility and decreased obesity rates, again controlling for
spatial correlation, socioeconomic attributes, and physical activity rates.

We also demonstrate how the choice-based accessibility metric could potentially 
be expanded to account for other elements of a park's attractiveness by 
introducing the number of tweets emanating from the park during 
(WE NEED TO DESCRIBE THE PERIOD). The paper concludes with a discussion of
opportunities for future research.

@@

\begin{table*}
  \caption{Commonly cited benefits of parks and greenspaces}
  \label{tab:parkbenefits}
\begin{tabular}{lp{11cm}}
\toprule
Category & Summary of Benefits\\
\midrule
Physical Health & Provide clean drinking water \citep{Benedict2006}\\
 & Promote faster healing in hospitals \citep{Akbari2001}\\
 & Reduce heat-related mortality \citep{Stone2006}\\
 & Reduce incidence of cardiovascular-related mortality \citep{Mitchell2008}\\
 & Improved air quality and related reductions in respiratory-related mortality \citep{Lovasi2008}\\
\midrule
Mental Health & Reduce stress and mental fatigue \citep{Wolch2014}\\
  & Reduce aggression \citep{Kuo2001a}\\
  & Enhance emotional and cognitive development\\
  & Improve behavioral outcomes in youth \\
\midrule
Social Health & Enhanced community aesthetics\\
 & Reduce crime \citep{Kuo2013,Wolfe2012}\\
 & Increase social interaction \citep{Sullivan2004}\\
\midrule
Economic Health & Provide ecosystem services\\
 & Increase residential property values and municipal property tax revenues\\
 & Attract more shoppers and increase economic activity to commercial districts \\
\bottomrule
\end{tabular}
\end{table*}

@@

When evaluating the impacts of parks and greenspaces on health outcomes at a
sub-metropolitan level, one of the fundamental challenges researchers face is
selecting a measure of accessibility. In a comprehensive meta-analysis of
published studies that measure active accessibility (accessibility using
non-motorized travel modes including walking and cycling), \citet{Vale2016}
identified four broad categories of studies based on the metric employed:
\begin{description}
  \item[Distance-based]{Account only for the Euclidean distance between origins
  and destinations}
  \item[Infrastructure-based]{Explicitly incorporate
  relevant transportation networks like roads and sidewalks to more accurately
  measure travel time and distance}
  \item[Gravity-based]{Incorporate travel impedance
  measures to model accessibility as a function of a destination’s attractiveness}
  \item[Walk-score]{Similar to Gravity-based, with the impedance measure
  explicitly designed around walking}
\end{description}

Importantly, \citeauthor{Vale2016} acknowledge that there is not yet a
consensus on the most appropriate accessibility metric to use in a given
setting, noting that ''ways to measure active accessibility are as varied as the
number of scholars the measure them.'' This is at least partly because
each method has inherent strengths and weaknesses.
Distance is an inherently continuous phenomenon, but software tools ease and enable
buffer analyses where distance becomes a binary phenomon of somewhat arbitrary
extent. \citet{Logan2017} note that these commonly used approaches can also lead
researchers to overlook access-poor populations.
Infrastructure-based distances can vary widely
depending on which modes of travel are considered. a highway network may not
adequately capture trails and bike paths.
Similarly, gravity-based measures may not always account for surrounding land
uses when considering the attractiveness or impedance of a destination; the
findings of \citet{Pretty2005} and other suggest unpleasant pedestrian routes
attenuate perceived travel costs.

Though there is no shortage of possible accessibility metrics, in this paper
we wish to present and apply a technique that is explicitly based in the choices
of individuals as they consider how to access parks.

@@

\subsection{Data}

@@

This study uses data available to the public from a variety of federal and state
data agencies. The datasets, as well as the analysis code, is available on GitHub
at \url{https://github.com/boydnpb/park_access_new.git}
The primary dataset is a geographic polygons shapefile of Census tracts in
New York City. We appended relevant sociodemographic data for each tract level
from the American Community Survey 2011-2015 5-year estimates. Data on physical
activity participation rate and obesity rates for each tract are available from
the Centers for Disease Control and Prevention’s 500 Cities Project (WE NEED A CITATION).
After removing tracts with missing population information or outlying and unusual
characteristics, we have Sexpr{nrow(tracts)} complete cases. Table
\ref{tab:tractsdata} presents key descriptive statistics for these data.

@@

In a destination choice framework, the tracts represent the "origins" and
"destinations" are parks in New York City.
We retrieved a shapefile of public parks and greenspaces within New York City’s
municipal boundaries and checked it for accuracy and relevance (WE NEED A CITATION).
Upon inspection,
we removed several facilities that do not qualify as publicly accessible green
space, such as Yankee Stadium and its surrounding parking lots. We also removed
parks of less than half an acre in size, as these appear to be predominantly
vacant lots or parking strips rather than legitimate public green space. This
leaves us with \Sexpr{nrow(parks)} parks. It is worth noting that the particular
dataset classifies specific facilities within larger parks as independent
features: baseball fields within Central Park, for example, are themselves
delineated green spaces. We elect to retain these independent features as they may
generate additional physical activity participation aside from the containing 
park.

@@

We predict the rate of physical activity ($y$) in a census tract as a
function of the tract's sociodemographic characteristics and choice-based
accessibility to parks with the following  specification:
\begin{equation}\label{eq:themodel}
 y_i = f(\vect{x}_i, CS_i, g(W, \vect{y}, \vect{X}))
\end{equation}
where $\vect{x}_i$ is a vector of tract-level sociodemographic attributes,
$CS_i$ is a choice-based accessibility measure for the tract computed from
Equation \ref{eq:cs} and $g(W, \vect{y}, X)$ represents the impact of spatial
neighborhood effects on the outcome.

@@

The researcher must assert $W$ {\em a priori}, though there are several
common specifications \citep{Dubin1998}. In this study we specify that tracts
with population-weighted centroids located within 1.8 Euclidean miles of each 
other are 
considered neighbors, and the strength of the relationship is the inverse of 
the distance between them:
\begin{equation}\label{eq:weightsrule}
W_{ij} = \begin{cases}
  {\frac{1/d_{ij}} {\sum_{k=1}^n( 1/d_{ik})}} & \text{for $d_{ij} \leq 1.8$ miles}\\
  0  & \text{for $d_{ij} > 1.8$ miles}
  \end{cases}
\end{equation}
<<weights, warning = FALSE>>=
pop_weighted_centroids <- read_csv("data/CenPop2010_Mean_TR36.csv") %>%
  mutate(geoid = str_c(STATEFP, COUNTYFP, TRACTCE))
pop_weighted_centroids <- left_join(tracts@data, pop_weighted_centroids, by = "geoid") %>%
  dplyr::select(geoid, LONGITUDE, LATITUDE) %>%
  st_as_sf(crs = 4326, coords = c("LONGITUDE", "LATITUDE")) %>%
  st_transform(2263)

tracts.dnn <- dnearneigh(gCentroid(as(pop_weighted_centroids, "Spatial"), byid = TRUE),
                         0, 1.8 * 5280)
dists <- nbdists(tracts.dnn, gCentroid(tracts, byid = TRUE))
dists.inv <- lapply(dists, function(x) 1 / x)
W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv,
              zero.policy = TRUE, style = "W")
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
@
This is a similar specification to then one \citet{tra_autoregression_paper} 
used in a study of home prices in Atlanta. We selected this specification after 
comparing overall model likelihoods between it and an adjacent (queen)
tract specification.

@@

Extant destination choice models used in practice typically use travel time in
minutes as a travel impedance term, and employment by sector as a size term or
attraction component. Typically such models handle recreational trips together with
other non-work and non-school trips, and we therefore can find no previously
estimated coefficients using size terms relevant to park acreage or amenities.
Given this gap in the literature, we instead assert plausible values for 
$\beta$ to generate the choice-based accessibility statistic used in this study.

@@

@@

The functional form of the accessibility statistic is adapted from 
Equation \ref{eq:v_sd} by log-transforming first the distance (Euclidean, in miles) 
between the park boundaries and population-weighted tract centroids and second the 
park size (in acres).
\begin{equation}\label{eq:v_logged}
V_{ij} = \log(size_j)\lambda_s + \log(distance_{ij})\lambda_d
\end{equation}
We then calculate the consumer surplus $C$  (log-sum of the exponentiated 
utilities) for each tract and standardize the result,
\begin{equation}\label{eq:v_logged}
C_i' = \frac{C_i - \bar{\vect{C}}}{sd(\vect{C})}
\end{equation}

We initially estimated potential values of the $\lambda$ coefficients by
applying a limited-memory, box-constrained optimization algorithm 
maximizing the model log-likehood.\footnote{Using the {\texttt nlm} function
in R \citep{RCoreTeam2018}} The constraint required that the coefficient on
size be positive and that on distance negative; all else equal, we assert people
will prefer to use larger parks and parks that are nearer to their residence. This
resulted in $\lambda_d = -1.98$  and $\lambda_s = 0.000$. Though the 
``most likely''
parameter value, in this case it was unsatisfactory for two reasons: first,
our prior assertion that park size is a valuable attribute of a park, and second
the observation that with these maximum likelihood values tracts bordering on 
the corners of
Central Park were measured with poor overall accessibility. We subsequently 
adjusted the $\lambda_s$ value to $0.3$; the relative ratio of the coefficients 
implies that all else equal, an individual would travel 6.6 times further to
access a park twice as large.

@@

Figure \ref{fig:map} shows a map of New York City with each tract highlighted
based on its relative accessibility score. The most continuous region of good park 
access is in upper Manhattan and the Bronx, bracketed by Central Park and the
Bronx River. Conversely, some of the poorest-accessibility areas are in 
Brooklyn tracts not immediately adjacent to Prospect Park. Because the 
accessibility statistic is normalized, the worst values are slightly below $-3$, 
the best somehere above $3$.

@@

The other two models presented in Table \ref{tab:pa_models} include
the log-sum accessibility statistic described in Section
\ref{subsec:accessibility}  added as a predictor. In both income specifications,
the access logsum is positively correlated with physical activity rates; all else
equal, people in tracts with higher accessibility to parks report higher rates of
physical activity. The estimated value of this coefficient and its standard
error is effectively the same with both representations of income, though in the
log representation the estimated $t$-statistic technically passes the $0.1$ level.
This is suggestive evidence only from a statistical perspective, but it deserves
comment. Taking a compromise value of $0.10$ between the two models, the data
suggest going from the least-accessible ($-3.0$) to the most-accessible ($3.0$) 
tract implies a $0.6$ percentage-point rise in physical activity rates, though
with a wide confidence interval around that estimate.

@@

\begin{table*}
  \caption{SEM Coefficients Predicting Physical Activity Rates}
  \label{tab:pa_models}
<<pamodelchart, results="asis">>=
termnames <- c("(Intercept)", "log(density)" ,
               "Full-time workers", "College-educated",  "Single Adults",
               "Share of children (0-17)", "Share of young adults (18-29)",
               "Share of seniors (65+)", "Black population share",
               "Asian population share",
               "Hispanic population share", "Other Minorities",
               "Share high income", "Share low income",
               "$\\lambda$", "$\\log($Income$)$",
               "Access logsum")
texreg(pa_models, digits = 4, table = FALSE,
       booktabs = TRUE, use.packages = FALSE,
       custom.coef.names = termnames,  stars = c(0.001, 0.01, 0.05, 0.1))
@
\end{table*}

<<obesity_models>>=
obesity_models <- lapply(pa_models, function(model){
  update(update(model, obesity ~ . + physact))
})

@@

<<screen_obese_models, eval = FALSE>>=
screenreg(obesity_models, digits = 4, table = FALSE,
          stars = c(0.001, 0.01, 0.05, 0.1) )
@

We now consider the impacts of a model where the dependent variable is
the {\em obesity} rate, and physical activity becomes an independent covariate
alongside the controlling variables and the accessibility logsum variable. 
Table \ref{tab:obese_model} presents the estimated coefficients for both
income specifications, with and without the accessibility logsum. As in the 
physical activity models, the coefficients are largely significant and
in the expected sign. The accessibility coefficient has practically the same 
effect as in the physical activity model: moving from poor to excellent parks 
access lowers the changes the expected obesity rate by around half a percentage
point. In this case, however, the parameter $p$-value is lower than the 
conventional $0.05$ level in each income representation.

\begin{table*}
  \caption{SEM Coefficients Predicting Obesity Rates}
  \label{tab:obese_models}
<<obesemodelchart, results="asis">>=
termnames <- c("(Intercept)", "log(density)" ,
               "Full-time workers", "College-educated",  "Single Adults",
               "Share of children (0-17)", "Share of young adults (18-29)",
               "Share of seniors (65+)", "Black population share",
               "Asian population share",
               "Hispanic population share", "Other Minorities",
               "Share high income", "Share low income",
               "$\\lambda$", "$\\log($Income$)$",
               "Access logsum")
texreg(obesity_models, digits = 4, table = FALSE, 
       booktabs = TRUE, use.packages = FALSE,
       custom.coef.names = termnames,  stars = c(0.001, 0.01, 0.05, 0.1))
@
\end{table*}

\subsection{Additional Amenities}

As discussed when presenting the choice-based accessibility metric above,
a key benefit it offers is the natural way in which park amenities beyond simply size
can be accomodated. For example, the number of tweets emanating from a park
might be seen as a measure of the park's popularity, or a proxy for its use. It 
may be construed that parks with high popularity or use contain other amenities
that encourage residents to use the park space, raising physical activity rates
and lowering obesity rates beyond what would be expected with the park's size
and proximity alone. It it reasonable to question whether park size and twitter
activity are highly correlated, and thus would result in a double-counting of
park size in the accessibility statistic. In our 
data the number of tweets is positively but only loosely correlated  with park 
size in our data ($\rho = \Sexpr{cor(parks$log_size, parks$log_tweets)}$), indicating
that the Twitter data in fact could provide new information or proxy for the 
desired amenities.

To test this hypothesis, we can use the twitter data described earlier
and suggested in Equation \ref{eq:v_sdt}. In this application, we again 
log-transform all the components of utility:
\begin{equation}\label{eq:v_logsdt}
V_{ij} = \log(size_j)\lambda_s + \log(distance_{ij})\lambda_d + g(tweets_j)\lambda_t
\end{equation}
where $g(x)$ is a Yeo-Johnson transformation to preserve cases where $log(0)$
would be otherwise undefined. As before, there is little information by which to
determine the values of $\lambda$ in this utility specification; we use the
previous values with the addition of $\lambda_t = 0.1$. The ratio between the 
utility coefficients implies residents would travel almost twenty times as far or
use a park three times smaller if it had twice the twitter activity, all else 
equal.

Figure \ref{fig:tweets_map} shows the percent change in the normalized log
sum statistic after including the twitter infromation. There is not a recognizable
overarching pattern to the changes, though tracts immediately surrounding 
Prospect Park and Central Park gain even more relative accessibility, and tracts
in midtown Manhattan, Queens, and southern Bronx tend to lose some.

<<tweets_map, echo=FALSE, message=FALSE, warning=FALSE>>=
library(ggmap)
map <- ggmap(get_map(unname(st_bbox(tracts_sf)), source = "stamen", maptype = "toner-lite"),
             extent = "device")
map +
  geom_sf(data = tracts_sf %>% 
            mutate(diff = tweets_ls - access_ls, 
                   pct_diff = diff / access_ls * 100), 
          inherit.aes=FALSE,
          aes(fill = cut(pct_diff, quantile(pct_diff, 
                                            probs = seq(0, 1, by = 0.1)))),
          alpha = 0.8, color = NA) +
  scale_fill_brewer("Percent Change", palette = "PiYG")
@
  \caption{Percent change in relative accessibility when accounting for Twitter 
  activity.}
  \label{fig:tweets_map}
\end{figure*}

<<tweets_models>>=
tweets_models <- list(pa_models[[3]], pa_models[[4]], 
                      obesity_models[[3]], obesity_models[[4]]) %>%
  lapply(function(model){
    update(update(model, . ~ . -access_ls + tweets_ls))
  })
@

Table \ref{tab:tweets_models} presents the estimated coefficients relating
accessibility to obesity and physical activity rates, with and without the 
inclusion of Twitter data. In all four cases, including twitter information in
the accessibility statistic tempers the strength of the relationship with the
dependent variable and modestly widens the standard error without substantively
affecting the significance of the test statistics.  
From this limited example,
it appears Twitter activity does not enhance the ability of parks to induce 
physical activity rates or lower obesity rates, though further investigation 
of this and other park amenities would certainly be warranted.

<<tab:tweets_models, results="asis">>=
names(tweets_models) <- c("Physical Activity: High and Low Income", 
                          "Physical Activity: log(Income)",
                          "Obesity: High and Low Income", "Obesity: log(Income)")
names(pa_models)[3:4] <- c("Physical Activity: High and Low Income", 
                           "Physical Activity: log(Income)")
names(obesity_models)[3:4] <- c("Obesity: High and Low Income", 
                                "Obesity: log(Income)")
lapply(c(tweets_models, pa_models, obesity_models), function(model){
  s <- summary(model)
  as_data_frame(s$Coef) %>%
    mutate(term = rownames(s$Coef)) %>%
    select(term, estimate = Estimate, std.error = `Std. Error`, 
           statistic = `z value`, p.value = `Pr(>|z|)`)
}) %>%
  bind_rows(.id = "model") %>%
  filter(term %in% c("tweets_ls", "access_ls")) %>%
  separate(model, c("y", "income"), ": ") %>%
  mutate(term = ifelse(term == "tweets_ls", 
                       "Tweets, Size and Distance", "Size and Distance")) %>%
  arrange(desc(y), income, term) %>%
  select(income, term, estimate, std.error, p.value) %>%

  kable(escape = FALSE, digits = 4,
        table.envir = "table*", booktabs = TRUE,
        caption = "Estimated Relationship between Accessiblity and Outcomes",
        col.names = c("", "Accessibility Components", "Estimate", "Std. Error",
                      "$p$-value")) %>%
  kable_styling() %>%
    group_rows("$y = $Physical Activity", 1, 4) %>%
    group_rows("$y = $Obesity", 5, 8)
@

\section{Limitations and Future Research Direction}

We readily acknowledge limitations in this study. As in any study conducted 
with areal data, we at risk of falling victim to the ecological inference 
fallacy, where aggregate statistics mask or contradict disaggregated or 
individual-level trends. A large-sample survey of individuals in New York City,
including measured physical activities and obesity would always be prefferable
to the tract-level data used in this study. It would be also be
preferrable to have obtained the $\lambda$ accessibility utility coefficients 
from a high-quality survey of leisure destination choice rather than
asserting them to match our prior expectations of what constitutes quality
park access. An ideal survey to address the question would incorporate both sets
of questions: physical activity and health data on one hand and park use (including
which parks were used and how frequently) on the other. As no such dataset
exists to our knowledge, this tract-level aggregate analysis with asserted 
utility coefficients is the possibility that remains.

This paper presents a holistic accessibility statistic that could, in theory,
accommodate many attributes of the destination parks as well as the people who 
might use them. As an illustration: the park-going population could be separated
into at least four delineated clusters, each preferring different amenities of a 
park: 
\begin{itemize}
 \item{runners and cyclists: long, interesting trail systems}
 \item{sports players: soccer fields, basketball courts, or baseball diamonds}
 \item{families with small children: water features and playgrounds}
 \item{casual users: water features, gardens, performances, etc.}
\end{itemize} 
An analyst could then compute the accessibility logsum for each cluster with
different utility values for each park's amenities, and obtain a measure of
a neighborhood's accessibility to park features that its residents most care 
about. In this paper, we proceed only incrementally beyond this theory by 
adding Twitter activity as an an element of a park's attractiveness above and
beyond its size. Exploring additional amenities or market segmentation strategies
could provide a more definitive understanding of the relationship between park 
accessibility and health outcomes.

Finally, this study is primarily focused on the hypothesis that accessibility to
parks encourages physical activity, which in turn reduces obesity. There are a 
multitude of other hypotheses that might be proposed and tested with the basic
methodology we have employed here, or competing explanations for the outcomes we
have observed. It is distinctly possible, for instance, that individuals who wish
to exercise regularly in parks choose to live near them; this could potentially
explain why the observed effects of accessibility seem partially dependent on
the representation of income in our econometric model. Controlling for this
potential self-selection effect would be necessary to isolate the exogenous
impacts of park access on obesity or other health outcomes. And regarding these
other variables: this study did not consider potential relationships between park
access and hospitalization rates, life expectancy, respiratory disease, 
mental health, or any number of potential beneficial outcomes hypothesized 
or explored in the existing literature. Exploring these connections and their
underlying mechanisms should be a priority as city planners and urban architects
attempt to improve the quality of life of urban residents in the future.
